Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-14 manuscript/main.tex
adjoint proved

First, $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$ 
maps  

@@

Next, $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$
maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:

@@

@@

	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
\begin{proposition}[Existence of Maximizer for Covariance]\label{proposition: eigenanalysis} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
	\begin{equation*} 
		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
		\end{equation*} 
	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
\end{proposition}
	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

@@

@@

\section{Proof of Proposition \ref{proposition: eigenanalysis}}\label{section:proof:proposition: eigenanalysis}
\begin{proof}
	content...
\end{proof}
	Before we prove Proposition \ref{proposition: eigenanalysis}, we state and prove the following lemma:
	\begin{lemma}
		$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^*$.
	\end{lemma}
	Proof.

	\noindent First, we have:
	\begin{equation*}
		\langle \mathcal{C}_{YW} \mathbf{h}, d \rangle = E\{ \langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} d
	\end{equation*}
	Also, we have:
	\begin{equation*}
		\langle \mathbf{h}, \mathcal{C}_{WY} d \rangle_{\mathcal{H}} = \langle \mathbf{h}, E(Y\mathbf{W})d \rangle_{\mathcal{H}} = E \langle \mathbf{h}, Y \mathbf{W} d \rangle_{\mathcal{H}}  = E\{ \langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} d.
	\end{equation*}
	Thus, $\langle \mathcal{C}_{YW} \mathbf{h}, d \rangle =  \langle \mathbf{h}, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}$, and this implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^*$.

>>>>

\begin{lemma}\label{lemma:cross_cov_operator}
Define $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$,
which	maps  

@@

	Next, define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:

@@

Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.

@@

	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
\begin{theorem}[Population PLS]\label{proposition: eigenanalysis} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
	\begin{equation*} 
		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
		\end{equation*} 
	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
\end{theorem}
	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

@@

	\section{Proof of}

	\subsection{Proof of Lemma \ref{lemma:cross_cov_operator}}\label{section:proof:lemma:cross_cov_operator}
For $h \in \mathcal{H}$ and $d \in \mathbb{R}$, we have:
	\mathcal{C}_{YW} h, d \rangle 
	[
	] 	 \,  d
%%%%%%%%%%%%%%%%%%
\mathbb{E} \langle   Y_1 W_1 d , \, h\rangle_{\mathcal{H}} 
 = \langle h, \, \mathbb{E}[Y_1 W_1 d   ]\rangle_{\mathcal{H}}
 \langle h, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}
Thus, we have $\langle \mathcal{C}_{YW} h, d \rangle =  \langle h, \mathcal{C}_{WY} d \rangle_{\mathcal{H}}$, which implies $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
	This completes the proof of Lemma \ref{lemma:cross_cov_operator}.

@@

\section{Proof of Proposition \ref{proposition: eigenanalysis}}\label{section:proof:proposition: eigenanalysis}
